---
title: "r_int_day_1_r_operator"
author: "Nicholus Tint Zaw"
date: "2022-10-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Content 

Types of the operator in R language 

1. Arithmetic Operators
1. Logical Operators
1. Relational Operators
1. Assignment Operators
1. Miscellaneous Operator


referenace: https://www.geeksforgeeks.org/r-operators/ 


## Arithmetic Operators 

### Addition operator (+): 

```{r addition}

1 + 1

c(1, 3, 5) + c(4, 6, 8)

```

### Subtraction Operator (-): 

```{r substr}

569 - 456

c(4, 69, 20) - c(34, 45, 200)


set.seed(2435)

x <- sample(1:10, 3, replace=TRUE)
y <- sample(1:10, 3, replace=TRUE)

x
y


x - y

```

### Multiplication Operator (*): 

```{r multipli}

4 * 5

x * y

```

### Division Operator (/): 

```{r div }
30/3

y/x

```

### Power Operator (^): 


```{r power}

690 ^ 0 

x ^ 1

x ^ y 

```

# Modulo Operator (%%): 

```{r}

22%%7

x %% 3


x %% y 

```



## Logical Operators 


### Logical AND operator (&):


```{r logicand}

random <- sample(1:20, 10, replace = TRUE)

random

random >= 3 & random < 10

```


### Logical OR operator (|): 

```{r logicalor}

random
random > 3 | random < 10 # why all TRUE? 

```


## Relational Operators 


```{r relational}

# greater than
1 > 0

c(c, y)

# greater than and equal to
x >= y


# less than 
5 < 2

x < y

# less than and equal to 
5 <= 10

x 
y
x <= y 


# equal to
1 == 0 # note: it is double equal 

1 == 1


# not equal to 
1 != 0 

0 != 0


```



## Assignment Operators 

```{r assign}

x <- 1 

i <- c(1, 3, 5)

y <- sample(100:200, 5, replace = TRUE)

c(x, i, y)

```



## Miscellaneous Operator 

### %in% Operator: 

```{r inope}
# with numeric vector
x <- c(1, 5, 7, 0, 10)

0 %in% x


15 %in% x


# with string vector 
strvector <- c("A", "B", "C", "D")

"A" %in% strvector

"G" %in% strvector

```



